\cvsection{PROFESSIONAL EXPERIENCE}

\begin{cventries}

    \cventry
        {Software Engineer}
        {Cloudly Infotech Ltd.}
        {Hybrid - Dhaka, Bangladesh}
        {January 2025 - Present}
        {
            \begin{cvitems}
                \item {Developed full-stack \textbf{TypeScript} features for an ML/AI-powered telecom network optimization platform, building a scalable dashboard with Next.js and Zustand while authoring type-safe API integration layers consumed by Python ML backend services.}
                \item {Designed and implemented advanced data visualization with interactive real-time charts displaying network performance metrics and ML model predictions for telecom operators.}
                \item {Engineered \textbf{TypeScript} REST API clients with strict type contracts, efficient caching strategies, and optimized data fetching patterns to manage large-scale telecom network datasets.}
                \item {Developed industry-grade machine controller software with real-time bidirectional communication using \textbf{TypeScript}, Next.js, and WebSocket integration for manufacturing operations.}
                \item {Containerized frontend infrastructure with Docker and deployed across AWS environments, optimizing CI/CD pipelines and build performance.}
                \item {Established TypeScript-first component architecture and design system standards, ensuring type safety and maintainability across multiple dashboard applications.}
            \end{cvitems}
        }

    \cventry
        {Contractual \& Part time}
        {Freelance Web Engineer}
        {Remote - Dhaka, Bangladesh}
        {January 2015 - Present}
        {
            \begin{cvitems}
                \item {Architected and delivered full-stack \textbf{TypeScript} applications using Node.js/Express backends and React/Next.js frontends for clients across diverse industries.}
                \item {Designed and implemented RESTful APIs with TypeScript and ExpressJS, integrating PostgreSQL and Firebase data stores with validated, type-safe data models.}
                \item {Developed Python automation scripts and data processing utilities to complement TypeScript-based systems and streamline backend workflows.}
                \item {Planned and engineered scalable web services applying modern TypeScript tooling across the full development lifecycle from API design to deployment.}
            \end{cvitems}
        }

    \cventry
        {Senior Front-End Engineer}
        {Curotec}
        {Remote - Pennsylvania, USA}
        {June 2022 - May 2023}
        {
            \begin{cvitems}
                \item {Developed and delivered 5+ industry-standard web applications using \textbf{TypeScript}, ReactJS, NextJS, and Laravel, enhancing client satisfaction and achieving a 25\% increase in user engagement.}
                \item {Ensured seamless user experiences with 100\% cross-browser compatibility and performance optimizations, resulting in a 20\% increase in performance scores.}
                \item {Resolved complex issues, enhanced operational efficiency by 30\%, and consistently delivered exceptional service, contributing to a 25\% increase in customer satisfaction.}
            \end{cvitems}
        }

    \cventry
        {Front-End Engineer}
        {Reformed Tech}
        {Dhaka, Bangladesh}
        {June 2021 - July 2022}
        {
            \begin{cvitems}
                \item {Designed and implemented robust Content Management Systems, enhancing client interface efficiency by 40\% and reducing content update times by 30\%.}
                \item {Took concepts and produced design mock-ups and prototypes to strengthen designs, enhance user experiences, and improve site interactions.}
                \item {Performed security maintenance and patching on the website interface, ensuring 99.9\% uptime and safeguarding post-launch viability.}
                \item {Conducted unit testing and resolved issues in web applications, achieving a 95\% bug resolution rate and enhancing overall application stability.}
            \end{cvitems}
        }

    \cventry
        {Front-End Engineer}
        {XpeedStudio}
        {Dhaka, Bangladesh}
        {May 2020 - May 2021}
        {
            \begin{cvitems}
                \item {Contributed to creating powerful WordPress plugins to aid users build websites using Elementor.}
                \item {Created web-based admin dashboards to manage plugin administrative tasks.}
                \item {Created several WordPress themes published on community markets.}
            \end{cvitems}
        }

\end{cventries}

\cvsection{INTERNSHIPS}

\begin{cventries}

    \cventry
        {Intern Software Engineer}
        {Bangladesh Venture Capital Ltd.}
        {Dhaka, Bangladesh}
        {January 2018 - March 2019}
        {
            \begin{cvitems}
                \item {Developed a virtual currency wallet application for in-campus facility transactions within my university.}
                \item {Gained hands-on experience while collaborating with a team to deliver a secure and user-friendly application.}
                \item {Prepared project presentations and reports to assist senior staff.}
                \item {Participated in workshops and presentations related to projects to gain knowledge.}
            \end{cvitems}
        }

\end{cventries}
